---
title: "Futher Analysis"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
```

## Mean_variance Relation


```{r echo=FALSE}
GLM_data_freq=read.csv(file="F://Project_doc//data file//GLM_data_freq_1.csv", sep=",",header=T)
with(GLM_data_freq, c(mean = mean(CLAIM_COUNT), var = var(CLAIM_COUNT), ratio = var(CLAIM_COUNT) / mean(CLAIM_COUNT)))

```

## Histogram of CLAIM DATA and transformed data

```{r , echo=FALSE}
attach(GLM_data_freq)
t=factor(CLAIM_COUNT,levels=0:20)
clm.tab=table(t)
clm.tab
par(mfrow=c(1,2))
barplot(clm.tab, xlab = "Number of CLAIMS", ylab = "Frequency",col = "lightblue")

abline(v = mean(CLAIM_COUNT), col = "red", lwd = 3)
ci <- mean(CLAIM_COUNT) + c(-1, 1) * sd(CLAIM_COUNT)
lines(x = ci, y = c(-4, -4), col = "red", lwd = 3, xpd = TRUE)

barplot(clm.tab , ylab = "log(Frequency)", xlab = "NUmber of CLAIMs", col = "lightblue", log = "y")
abline(v = mean(CLAIM_COUNT), col = "red", lwd = 3)
ci <- mean(CLAIM_COUNT) + c(-1, 1) * sd(CLAIM_COUNT)
lines(x = ci, y = c(-4, -4), col = "red", lwd = 3, xpd = TRUE)
 
```

Barplots showing the frequency distribution of Number of Claim Count. 
Left: raw scale; right: a log scale makes the smaller counts more visible. The vertical red
lines show the mean and horizontal lines show mean ±1 standard deviation.
```{r,echo=FALSE}
library(ggplot2)
ggplot(GLM_data_freq, aes(VEHICLE_MAKE, CLAIM_COUNT )) + geom_jitter(position = position_jitter(h = 0.05)) +stat_smooth(method = "loess", size = 2, fill = "blue", alpha = 0.25)+ stat_smooth(method = "glm", color = "red", size = 1.25, se = FALSE) 
```

```{r,echo=FALSE}
tran_data=GLM_data_freq[which(GLM_data_freq$CLAIM_COUNT<20),]





obj2=glm(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP+offset(log(NCB_ADJ_POLICY_COUNT)), data=tran_data[,c(-1,-17)],family=poisson(log))


library(MASS)
obj4=glm.nb(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP+offset(log(NCB_ADJ_POLICY_COUNT)), data=tran_data[,c(-1,-17)])


library(effects)

plot(allEffects(obj4), band.colors = "blue", lwd = 1,
 ylab = "CLAIM_COUNT", main = "")
```

### neg

### Rootogram
The rootogram is a graphical tool associated with the work of J. W.
Tukey that was originally used for assessing goodness of fit of univariate distributions.
Here, we extend the rootogram to regression models and show that this is particularly useful for diagnosing and treating issues such as overdispersion and/or excess zeros in count data models. We also introduce a weighted version of the rootogram that can be applied out of sample or to (weighted) subsets of the data, for example, in finite mixture models.


```{r,echo=FALSE}
library(pscl)
zip2= zeroinfl(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP,data=tran_data,dist="poisson",link="logit", control=zeroinfl.control("BFGS"))


zinb4= zeroinfl(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP,data=tran_data,dist="negbin",link="logit", control=zeroinfl.control("L-BFGS-B"))


ctrl <- hurdle.control(method = "L-BFGS-B")
ctrl$reltol <- NULL
hrd_p2=hurdle(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP,data=tran_data,dist="poisson",zero.dist = "binomial",link="logit",control=ctrl)


ctrl <- hurdle.control(method = "L-BFGS-B")
ctrl$reltol <- NULL
hrd_nb4=hurdle(CLAIM_COUNT~CC_BAND_GROUP+VEHICLE_MAKE+FUEL_AGE_NILDEP,data=tran_data,dist="negbin",zero.dist = "binomial",link="logit",control=ctrl)
library(MASS)
library(countreg)
par(mfrow=c(1,2))
 countreg::rootogram(obj2, max = 20,main = "GLM: Poisson")
 countreg::rootogram(obj4, max = 20, main = "GLM: Negative-Binomial")
 rootogram(zip2, max = 20,main = "Zero Inflated Poisson")
 countreg::rootogram(zinb4, max = 20, main = "Zero Inflated Negative Binomial")
 rootogram(hrd_p2, max = 20,main = "Hurdle Poisson")
 countreg::rootogram(hrd_nb4, max = 20, main = "Hurdle Negative Binomial")

```
```{r}
obj2=glm(CLAIM_COUNT ~ CC_BAND_GROUP + AGE_FLOOR2 + FUEL_TYPE_GROUP + VEHICLE_MAKE + zero_dep_flag + offset (log (NCB_ADJ_POLICY_COUNT)),data=GLM_data_freq[,c(-1,-17)],family=poisson(log))


```
### hurdle model
